Appendix for 'Framing Effects in the Wild

### 2022-09-19 paper/appendix.Rmd
Bulk changes
- add table with example headlines
- replace code w functions

@@

@@

### Reichelt

@@

LTPDiD(return_table = T)

@@

(Association of Crime with migration attitude should be sigificantly higher in post-treatment-group)

@@

# define dv and conditioning variable
gles_p_long[["dv"]] <- gles_p_long[["1130_clean"]]
gles_p_long[["crime_att"]] <- gles_p_long[["2880h_clean"]]
gles_p_long$Individual <- gles_p_long$lfdn

inter <- 
  feglm(dv ~ post * treat * crime_att, 
        cluster = c("Individual"), 
        data = gles_p_long %>% 
          filter(!is.na(dv), !is.na(treat), !is.na(post), !is.na(crime_att)))

inter_cond <- 
  feglm(dv ~ post * treat * init_mig * crime_att , 
        cluster = c("Individual"), 
        data = gles_p_long %>% 
          filter(!is.na(dv), !is.na(treat), !is.na(post), 
                 !is.na(crime_att), !is.na(init_mig)))

inter_fe_cond <- 
  feglm(dv ~ post * treat * init_mig * crime_att | Individual, 
        cluster = c("Individual"), 
        data = gles_p_long %>% 
          filter(!is.na(dv), !is.na(treat), !is.na(post), 
                 !is.na(crime_att), !is.na(init_mig)))

inter_fe <- 
  feglm(dv ~ post * treat * crime_att | Individual, 
        cluster = c("Individual"), 
        data = gles_p_long %>% 
          filter(!is.na(dv), !is.na(treat), !is.na(post), !is.na(crime_att)))

modelsummary(
  list(
    inter, inter_fe, inter_cond, inter_fe_cond
  ),
  stars = T,
  # coef_map =
  #   c("postTRUE:treatTRUE" = "ATE",
  #     "postTRUE:treatTRUE:crime_att" = "ATE X Crime Attitude",
  #     "postTRUE:treatTRUE:init_mig:crime_att" = "ATE X Crime Attitude X \nInitial Migration Attitude"),
  gof_omit = "^(?!R2.Pseudo|Num|Std|FE)", 
  output = "markdown"
)

rm(gles_p_long, inter, inter_fe, inter_cond, inter_fe_cond)

>>>>

```{=tex}
\begin{table}
\centering
\begin{tabular}{|p{12cm}|}
\hline
Final new years eve report of Cologne police: male groups identified \\ \hline
Police searching for Northern-african offender: asylum-raid in Dortmund! \\ \hline
Search in refugee home - mega-raid addressing asylum fraud \\ \hline
Two groups attacking each other - again bloody conflict in refugee shelter \\ \hline
Cabin fever! Violence! Mass brawls! This is behind the increase in refugee clashes \\ \hline
\end{tabular}
\caption{Headlines of five migration articles most likely to concern crime, according to BERT crime classifier. Translation by author.}
\label{tab:exampleArticles}
\end{table}
```

@@

```
## Crowding out

```{r crowdout}

CrowdOutEstimates(vis = T)

@@

@@

modelsummary::modelsummary(LTPDiD(return_table = T), output = "markdown", stars = T)

@@

@@

MigCrimeCorTable()
